% --------------------------------------------------------------------------- %
% --------------------------------------------------------------------------- %
\chapter{Summary and Conclusions}
\label {ch:conclusion}
% --------------------------------------------------------------------------- %
% --------------------------------------------------------------------------- %
In 2010, a search was performed with the first data taken at CMS~\cite{2010ZMETpaper}.
5 $\mathrm{fb^{-1}}$ of data was taken with a center of mass energy of 7 TeV.
No new physics was discovered in this dataset, and the search was performed again with the larger dataset taken in 2012~\cite{2012ZMETpaper}.
This dataset consisted of 20 $\mathrm{fb^{-1}}$ of data with a center of mass energy of 8 TeV.
The search was also extented to be sensitive to electroweak SUSY~\cite{2012ewk,2012ewkhiggs}.
There was no new physics discovered in any of these channels.
After 2012, the LHC was shut down for upgrades, and data taking resumed in 2015 with a higher center of mass energy of 13 TeV.

A search for new physics beyond the standard model was performed using data collected by the CMS detector in 2015.
No significant excess beyond the standard model background predictions was observed,
and upper limits were set on the cross section in the context of a SUSY model where two gluinos are pair produced,
and subsequently decay to quarks and a neutralino.
The neutralino then decays to a Z boson, and a gravitino in this model, where the gravitino is expected to be massless.
Models where the gluino has a mass range of 1050 to 1300 GeV are excluded by these results.
